---
title: "Week 8 Lab Notebook"
author: "Kellie Wills, Ph.D."
date: "5/19/2022"
output: github_document
---

```{r}

library(astsa)

```


## Read in data and create time series objects

```{r}

econseries = read.csv("../Week 3/uschange.csv")
cc = ts(econseries$Consumption, freq = 4, start = c(1970, 1))
inc = ts(econseries$Income, freq = 4, start = c(1970, 1))
sav = ts(econseries$Savings, freq = 4, start = c(1970, 1))

```

These are stationary series (% changes, so already differenced).

## Part 1. Regression of consumption on income
```{r}

plot(inc, ylab = "% change", ylim=c(-4, 4), main = "Income")

```

```{r}

plot(cc, ylab = "% change", ylim=c(-4, 4), main = "Consumption")

```

```{r}

plot(inc, cc, xlab = "% change income", ylab = "% change consumption")

```


```{r}

ccreg_wrong = lm(cc ~ inc)
summary(ccreg_wrong)

```

```{r}

plot(ccreg_wrong)

```

The usual residual plots look fine, BUT...

```{r}

acf2(ccreg_wrong$residuals)

```

What ARMA model to try for the errors? 

```{r}
reg_arma <- sarima(cc, 3,0,0, xreg = inc)
reg_arma
```


## Part 2. Regression of savings on income

```{r}

plot(inc, sav, xlab = "% change income", ylab = "% change savings")

```

Ordinary regression:
```{r}
incsav <- lm(sav ~ inc)
summary(incsav)
```

ACF/PACF residuals:
```{r}


```


## Part 3. Cross-correlation and lagged predictor

```{r}

ccf(x = inc, y = sav)

```

```{r}

lag2.plot(inc, sav, max.lag = 1, corr = TRUE)

```
 
# Make the time spans match up
```{r}

alldata = ts.intersect( inc, inclag1 = lag(inc,-1), sav )

```

# Ordinary regression
```{r}

sav_inclag_lm = lm(sav ~ inc + inclag1, data = alldata)
summary(sav_inclag_lm)

```

```{r}

acf2(sav_inclag_lm$residuals)

```


# What about consumption?

```{r}

ccf(x = inc, y = cc)

```




