---
title: "Week 4 Lab: Forecasting"
output: github_document
---

```{r, setup, message=FALSE}
library(astsa)
library(tseries)
library(forecast)
```

# US Exchange data
```{r}
econ.df <-  read.csv("../Week 3/uschange.csv")
econ.ts <- ts(data = econ.df$Consumption, start = c(1970,1), frequency = 4)
```

## Splitting into train and test data

Set test test as last 2 years of data
```{r}
train <- window(econ.ts, end = c(2014,3))
test <- window(econ.ts, start = c(2014,4))
```

## Forecast 1: Using AR3

```{r}
econ.for.ar3 <- sarima.for(train, n.ahead = 8, p=3,d=0,q=0)
lines(test,type='o')
```

### Checking predictions, standard error and accuracy metrics
```{r}
econ.for.ar3$pred
econ.for.ar3$se
accuracy(econ.for.ar3$pred, test)
```

## Forecast 2: MA3

```{r}
econ.for.ma3 <- sarima.for(train, n.ahead = 8, p=0, d=0, q=3)
lines(test, type='o')
```

### Checking predictions, standard error and accuracy metrics
```{r}
econ.for.ma3$pred
econ.for.ma3$se
accuracy(econ.for.ma3$pred, test)
```

# CAR Exports Data
```{r}
car.df <- read.csv("../Week 3/CAR_exports.csv")
head(car.df)
str(car.df)
```

Converting to time series object:
```{r}
car.ts <- ts(car.df, frequency = 1, start = c(1960))
plot(car.ts)
```

## Split into train and test set
```{r}
train.car <- window(car.ts, end = 2012)
test.car <- window(car.ts, start= 2012)
```

## Forecast: AR2
```{r}
car.for <- sarima.for(train.car, n.ahead = 5, p=2, d=1, q=0)
lines(test.car, type='o')
```

### Checking predictions, standard error and accuracy metrics
```{r}
car.for$pred
car.for$se
accuracy(car.for$pred, test.car)
```