---
title: 'DATA 598: Assignment 1'
author: "Hriday Baghar"
date: "April 28, 2022"
output:
  github_document: default
mainfont: Helvetica
monofont: Monaco
---

```{r, setup, message=FALSE}
library(fpp3)
library(astsa)
library(knitr)
```

# Model the US GDP series found in the global_economy dataset in package fpp3. See textbook section 9.7 for an example of working with this dataset.

Loading the dataset and extracting the required series.
```{r}
global_economy |>
  filter(Code == "USA") |>
  select(Country, Year, GDP) |>
  as_tsibble(index = Year) -> gdp.usa

kable(head(gdp.usa))
```

## 1. Plot the series [1 point].

```{r}
autoplot(gdp.usa, GDP)+
  ggtitle("Plot of US GDP Against Time")+
  labs(x = "Year")+
  scale_y_continuous(labels =  scales::dollar_format(suffix = " Trillion", scale = 1/1e12))
```

## 2. Determine whether the series is stationary; if not, take appropriate action [1 point].

This series is clearly non-stationary, as can be seen with the rising trend. We confirm this using a KPSS test:
```{r}
gdp.usa |>
  features(GDP, unitroot_kpss)
```
Since the p-value is < 0.05, we reject the null hypothesis that the data is stationary. 

We need to make this data stationary. We do this by applying a difference operation. Let us use the `unitroot_ndiffs()` function to check how many difference operations are required.

```{r}
gdp.usa |>
  features(GDP, unitroot_ndiffs)
```
Two differences are required based on this function. Let us check what happens with a first order difference operation:
```{r}
gdp.usa  |>
  autoplot(difference(GDP)) +
  labs(title = "First order differenced series", x="Year")

gdp.usa |>
  features(difference(GDP), unitroot_kpss)
```
It is clear that a first order difference still has some trend is non-stationary. The KPSS test supports this.

We take a second order difference and inspect it in a similar manner:
```{r}
gdp.usa  |>
  autoplot(difference(GDP, differences = 2)) +
  labs(title = "Second order differenced series", x="Year")

gdp.usa |>
  features(difference(GDP, differences = 2), unitroot_kpss)
```
Both the plot and the KPSS test support that the series is now stationary.

## 3. Include appropriate ACF and PACF plots and interpret them [1 point].

```{r}
gdp.usa |>
  mutate(diff.2 = difference(GDP, differences = 2)) |>
  gg_tsdisplay(diff.2, plot_type = "partial")
```

From the ACF and PACF plots we observe:

1. ACF exhibits sinusoidal-like behavior with a significant spike at lag 7
2. PACF has has a significant spike at lag 6 and none beyond that

Since the decay is sinusoidal in ACF and PACF has a spike at lag 6, an AR6 model looks like a good candidate for this series. We might explore an MA7 model to but we do not see a sinusoidal or exponential decay in the PACF, which is why AR6 seems to be a better choice.

## 4. Use sarima() to fit at least one model for the series [1 point].

```{r}
sarima(gdp.usa$GDP, p=6,d=2,q=0)
```
Let us use `fable` to fit the same model. We can also search for the best model based on the automatic search feature of the `ARIMA()` function.
```{r}
gdp.fit <- gdp.usa |>
  model(arima620 = ARIMA(GDP ~ pdq(6,2,0)),
        search = ARIMA(GDP))

gdp.fit |>
  pivot_longer(cols = -Country, names_to = "Model name", values_to = "Model") |>
  mutate(model.details = format(Model))

glance(gdp.fit) |> arrange(AICc) |> select(.model:BIC)
```
Interestingly, `ARIMA()` search finds MA2 to be a better fit.

Let us plot the resiudals from both models:
```{r}
gdp.fit |>
  select(arima620)|>
  gg_tsresiduals()

gdp.fit |>
  select(search) |>
  gg_tsresiduals()
```

## 5. Comment on the residual plots from sarima() [1 point].

From the `sarima()` plots, we can conclude that the residuals are white noise because:

- The ACF spikes are all non-significant
- The residuals have constant variance, although the end of the residual plot appears to have some departure from 0
- P-values from the Ljung-Box plot are all above the significance level, although lag 9 and 10 are somewhat close