---
title: "Week 3 Lab: Part 2"
output: github_document
---

```{r, message=FALSE}
library(tseries)
library(astsa)
library(forecast)
```

# Read CAR Exports data
```{r}
car.df <- read.csv("CAR_exports.csv")
head(car.df)
str(car.df)
```
Converting to time series object:
```{r}
car.ts <- ts(car.df, frequency = 1, start = c(1960))
plot(car.ts)
```

# Check for stationarity:

Above plot shows that the series is non-stationary, due to the downward trend. Let's do an extra test to make sure
```{r}
kpss.test(car.ts)
```
We see that the series is non-stationary based on p-value.

# Differencing
```{r}
car.diff.ts <- diff(car.ts, lag = 1)
plot(car.diff.ts)
```

Let's check for stationarity:
```{r}
kpss.test(car.diff.ts)
```
Series is stationary!

# Modeling series

```{r}
acf2(car.diff.ts)
```

We consider the following models:

- AR2: We see 2 significant spikes in the PACF
- MA3: We see significant spikes in ACF at lag 1 and 3. Even though 2nd spike is not significant, we should check it out

## AR2 model
```{r}
sarima(car.diff.ts, p=2,d=0,q=0)
```

Observations:

- ACF looks good - no significant spikes
- Ljung-box looks OK - some values are close to the line

## MA3 model

```{r}
sarima(car.diff.ts, p=0,d=0,q=3)
```

Residuals looks much better than AR2