---
title: "R Notebook"
output: github_document
---

```{r, setup, message=FALSE}
library(fpp3)
```

## Read ausbeer.csv and display it
```{r}
ausbeer.ts <- read.csv("ausbeer.csv") |>
  mutate(Qtr = yearquarter(Time)) |>
  select(Qtr, Production, -Time) |>
  as_tsibble(index = Qtr)

ausbeer.ts |>
  autoplot(Production)
```

## Checking for stationarity

Taking seasonal difference:
```{r}
ausbeer.ts |>
  mutate(seas.diff = difference(Production, lag=4)) -> ausbeer.ts
  
ausbeer.ts |>
  autoplot(seas.diff)

ausbeer.ts |>
  features(seas.diff, unitroot_kpss)
```

We reject the null hypothesis, this series is not stationary.

Applying a non-seasonal difference on the seasonally differenced series:
```{r}
ausbeer.ts |>
  mutate(s.ns.diff = difference(seas.diff, lag=1)) -> ausbeer.ts

ausbeer.ts |>
  autoplot(s.ns.diff)

ausbeer.ts |>
  features(s.ns.diff, unitroot_kpss)
```
This data is now stationary.

## Analyze ACF and PACF
```{r}
ausbeer.ts |>
  gg_tsdisplay(s.ns.diff, plot_type = "partial")
```
ACF:

- We see significant spikes at lag 1, 3 and 4
- Spike at lag 1 is likely indicative of non-seasonal MA
- Spike at lag 4 is likely indicative of seasonal MA
- We see spikes at lag 3 and 5 but they can be due to the autocorrelation at lag 1 and 4

PACF:

- We see significant spikes at lags 1 and 2 likely indicating non-seasonal AR2

Pro tip: Check for spikes within the first seasonal range to develop model intuition

## Model series

Splitting into train and test set
```{r}
train <- ausbeer.ts |> filter(Qtr < yearquarter("2008 Q3"))
test <- ausbeer.ts |> filter(Qtr >= yearquarter("2008 Q3"))
```

We model the series based on the ACF and PACF.

The model we choose will be (2,1,1)(0,1,1)4 because:

- Seasonal spike at lag 4
- Non-seasonal MA term at lag 1, non-seasonal AR terms at lag 1,2
- 1 seasonal and 1 non-seasonal difference

```{r}
fit <- train |> model(arima211011 = ARIMA(Production ~ pdq(2,1,1) + PDQ(0,1,1)))

fit |> gg_tsresiduals()
```
- Residuals appear to be white noise for the most part.

```{r}
glance(fit)
report(fit)
```
# Forecasting
```{r}

train |>
  model(arima211011 = ARIMA(Production ~ pdq(2,1,1) + PDQ(0,1,1))) |>
  forecast(h=8) |>
  autoplot(train)+
  geom_line(data = test, aes(x=Qtr, y=Production), color = "red", alpha=0.5)
```

